---
title: "Eyetracking"
output: html_document
date: "2023-11-06"
---
# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(sp)
library(stringr)
install.packages("jpeg")
install.packages("grid")
library(jpeg,grid)

setwd(".")
```

```{r}
# get a nice font
install.packages('extrafont')
library(extrafont)
font_import()
loadfonts(device = "win")
```

# AOI Clean up
```{r}
aoi <- read.csv("AOI_MAGNIFISO.csv")
aoi <- AOI_MAGNIFISO
aoi$Points <- gsub(";;", ":", aoi$Points)
aoi$Points <- gsub(";", ".", aoi$Points)
aoi <- subset(aoi,select=-c(Timestamp..ms.,Is.active))
aoi <- aoi[c(TRUE, FALSE), ]
for (row in seq(1,nrow(aoi))) {
  aoi$Task[row] <- strsplit(aoi$Group[row],"_")[[1]][3]
  aoi$Stimuli[row] <- strsplit(aoi$Group[row],"\\.")[[1]][1]
  print(paste0("completed ",row))
}
aoi <- subset(aoi, Task=="recog",select=AOI.Name:Stimuli)
write.csv(aoi,"AOI.csv")
```

## Clean up participant dataframes
```{r}
#find all files #remove merge
files <- list.files("Eye-tracking_data")

coloumns_to_remove <- c("Combined Event Source", "SlideEvent","StimType","Duration","CollectionPhase","SourceStimuliName","MarkerDescription","SceneType","ET_PupilLeft","ET_PupilRight","ET_TimeSignal","ET_DistanceLeft","ET_DistanceRight","ET_CameraLeftX","ET_CameraLeftY","ET_CameraRightX","ET_CameraRightY","ET_Distance3D","ET_HeadRotationPitch","ET_HeadRotationYaw","ET_HeadRotationRoll","ET_GazeDirectionLeftQuality","ET_GazeDirectionRightQuality","ET_EyelidOpeningLeft","ET_EyelidOpeningLeftQuality","ET_EyelidOpeningRight","ET_EyelidOpeningRightQuality","ET_LeftPupilDiameterQuality","ET_RightPupilDiameterQuality","Event Group","Event Label","Event Text","Event Index","Gaze X","Gaze Y","Interpolated Gaze X","Interpolated Gaze Y","Interpolated Distance","Gaze Velocity","Gaze Acceleration","Fixation Index by Stimulus","Fixation Start","Fixation End","Fixation Dispersion","Saccade Index by Stimulus","Saccade Start","Saccade End","ET_GazeLeftx","ET_GazeLefty","ET_GazeRightx","ET_GazeRighty")

for (file in files){
  start_time <- Sys.time()
  temp <- read.csv(paste0("Eye-tracking_data/",file))
  #find name
  ID_row <- which(temp[1] == "#Respondent Name")[1]
  ID <- temp[ID_row,2]
  
  #find row with #Data
  data_start_row <- which(temp[1] == "#DATA")[1]
  next_row <- data_start_row+1
  len <- nrow(temp)
  # remove everything from start row  to #Data row
  temp <- temp[next_row:len,]
  # use next row as header
  names(temp) <- temp[1,]
  # remove next row
  temp <- temp[-1,]
  # remove coloumns called
  temp <- temp[,!(names(temp) %in% coloumns_to_remove)]

  #add a coloumn called ID with information from 2 coloumn 4 row
  temp$ID <- ID
  # add a task, trial index, stimuli coloumn
  temp$Task <- NA
  temp$Trial_index <- NA
  temp$Stimuli <- NA
  
    #find relevant rows with imotions markers
    trial_start <-which(temp$MarkerType=="S")
    trial_end <- which(temp$MarkerType=="E")
    rows_to_remove <- c(trial_start, trial_end)
    recog=1
    act=1
    style=1
    for (i in seq(1,length(trial_start))){
        n_rows <- trial_end[i]-trial_start[i]
        event_name <- temp$MarkerName[trial_start[i]]
        task <- strsplit(event_name,"_")[[1]][3]
        stimuli <- strsplit(event_name,"\\.")[[1]][1]

        #add the same event_name to the the rows between trial_start and trial_end
        temp$Task[trial_start[i]:trial_end[i]] <- task
        
        #add the same stimuli to the the rows between trial_start and trial_end
        temp$Stimuli[trial_start[i]:trial_end[i]] <- stimuli
        temp$MarkerName[trial_start[i]:trial_end[i]] <- event_name

        #if the event_name is recog
        #add the same trial_index to the the rows between trial_start and trial_end
        if (task == "recog"){
            temp$Trial_index[trial_start[i]:trial_end[i]] <- recog
            recog <- recog+1
        }
        else if (task == "act"){
            temp$Trial_index[trial_start[i]:trial_end[i]] <- act
            act <- act+1
        }
        if (task == "style"){
            temp$Trial_index[trial_start[i]:trial_end[i]] <- style
            style <- style+1
        }
    }

    #remove rows without a MarkerName
    temp <- temp[!is.na(temp$Stimuli),]
    temp <- temp[-rows_to_remove, ]
    
    # Split the file name by underscores
    parts <- strsplit(file, "_")[[1]]

    # Keep the last part after splitting
    new_name <- tail(parts, 1)
    new_path <- file.path(output_folder, new_name)
    print(new_path)
    
    #save file to EOTP/ET-folder/Cleaning_up_dataframes/filename
    write.csv(temp, paste0("Cleaning_up_dataframes/",new_name))
    end_time <- Sys.time()
    duration <- end_time-start_time
    print(paste0("completed ",file, " in ", duration))
}
```

## Specific for day 17 where bison 4 is misspelled
```{r}
files <- list.files("Cleaning_up_dataframes")
#get only the files starting with 17
files <- files[grep("^17", files)]

for (file in files){
    start_time <- Sys.time()
    temp <- read.csv(paste0("Cleaning_up_dataframes/",file))
    #in temp rename all occurences of bison_11 to bison_4
    temp$Stimuli <- gsub("bison_11", "bison_4", temp$Stimuli)
    temp$MarkerName <- gsub("bison_11", "bison_4", temp$MarkerName)
    write.csv(temp,paste0("Cleaning_up_dataframes/",file))
    end_time <- Sys.time()
    print(paste0("Time to rename all occurences of bison_11 to bison_4 in ", file, ": ", end_time-start_time))
}
```

## Cross referencing aoi dataframe with participant dataframes
```{r}
#find all files #remove merge
files <- list.files("Cleaning_up_dataframes")

coloumns_to_save <- c("X","Row","ID","Task","Trial_index","Stimuli","Timestamp","MarkerName","Fixation.Index","Fixation.X","Fixation.Y","Fixation.Duration","Saccade.Index","Saccade.Amplitude","Saccade.Peak.Velocity","Saccade.Peak.Acceleration","Saccade.Peak.Deceleration","Saccade.Direction")

for (file in files){
  start_time <- Sys.time()
  temp <- read.csv(paste0("Cleaning_up_dataframes/",file))
  
  #check stimuli names
  #print(paste0(file, " has stimuli according to aoi dataframe: ", sort(unique(temp$Stimuli))==sort(unique(aoi$Stimuli))))
  #print(paste0(file, " has the same length of stimuli: ", length(unique(try$Stimuli))==length(unique(aoi$Stimuli))))

  # remove rows where marker type is E and S
  trial_start <-which(temp$MarkerType=="S")
  trial_end <- which(temp$MarkerType=="E")
  rows_to_remove <- c(trial_start, trial_end)
  temp <- temp[-rows_to_remove, ]
  # remove coloumns not in the list
  temp <- subset(temp,select = names(temp) %in% coloumns_to_save)
  
  #add a coloumn for AOI
  temp$AOI_hit <- NA
  temp$Timestamp_start <- NA
  temp$Timestamp_end <- NA
  
  #for each fixation check aoi
  uni_fix <- unique(temp$Fixation.Index)
  real_fix <- na.omit(uni_fix)
  
  for (fixation in real_fix){
    
    #for some reason this is empty
    first_row_index <- which(temp$Fixation.Index==fixation)[1]
    last_row_index <- which(temp$Fixation.Index==fixation)[length(which(temp$Fixation.Index==fixation))]

 
    #save timestamp start adn end in one row
    temp$Timestamp_start[first_row_index] <- temp$Timestamp[first_row_index]
    temp$Timestamp_end[first_row_index] <- temp$Timestamp[last_row_index]
    
    #something goes wrong here

    #get the stimulus
    stimulus <- temp$Stimuli[first_row_index]
    #get the fixation point
    fix_x <- temp$Fixation.X[first_row_index]
    fix_y <- temp$Fixation.Y[first_row_index]
    
    
    #check if the fixation is within an AOI
    aois <- filter(aoi, Stimuli == temp$Stimuli[first_row_index])

    fixation_point <- c(fix_x, fix_y)
    
    #for all aoi's check if the fixation is within the aois
    for (i in seq(1,nrow(aois))){ #virker ikke
        #get the points of the aoi
        string_points <- aois$Points[i]
        split_string <- strsplit(string_points, ":")
        number_of_points <- length(split_string[[1]])

        #create a matrix with the points
        points <- matrix(nrow = number_of_points/2+1, ncol = 2)
        for (j in seq(1:number_of_points)){
            #every other point is a x coordinate, the other is a y coordinate
            if (j %% 2 == 0){
                points[j/2,2] <- as.numeric(split_string[[1]][j])
            } else {
                points[(j+1)/2,1] <- as.numeric(split_string[[1]][j])
            }
        }
        points[number_of_points/2+1,] <- points[1,]
        
        # Check if the point is inside the polygon
        is_inside <- point.in.polygon(fixation_point[1], fixation_point[2], points[,1],points[,2])
        #print(paste0("fix ",aois$AOI.Name[i], " is ", is_inside))

        if (is_inside == 1){
          temp$AOI_hit[first_row_index] <- aois$AOI.Name[i]
        }else{
          temp$AOI_hit[first_row_index] <- "NA"
        }
    }
  }
    #save file
    write.csv(temp, paste0("AOI-updated-participant-dataframes/",file))
    
    #remove everything but filled rows for fixations
    temp <- temp[!is.na(temp$Timestamp_end),]
    temp <- subset(temp,select = -c(Saccade.Index:Saccade.Direction))
    #bind to grand df
    fixations_df <- rbind(fixations_df,temp)
    
    end_time <- Sys.time()
    duration <- end_time-start_time
    print(paste0("completed ",file, " in ", duration))
}
```

## Combine to grand fixation df
```{r}
fixations_df <- data.frame()

files <- list.files("AOI-updated-participant-dataframes")

coloumns_to_save <- c("X","Row","ID","Task","Trial_index","Stimuli","MarkerName","Fixation.Index","Fixation.X","Fixation.Y","Fixation.Duration","AOI_hit","Timestamp_start","Timestamp_end")

for (file in files){
  start_time <- Sys.time()
  temp <- read.csv(paste0("AOI-updated-participant-dataframes/",file))
  
  # remove coloumns not in the list
  temp <- subset(temp,select = names(temp) %in% coloumns_to_save)
  
  #remove everything but filled rows for fixations
  temp <- temp[!is.na(temp$Timestamp_end),]

  #bind to grand df
  fixations_df <- rbind(fixations_df,temp)
    
  end_time <- Sys.time()
  duration <- end_time-start_time
  print(paste0("completed ",file, " in ", duration))
}

write.csv(fixations_df,"collected_fixations_dataframe_GRANDIOSA.csv")
```

# Final cleaning
```{r} 
#load data first both fixations_df and AOI.csv
for (row in seq(1, nrow(fixations_df))){
    #get the stimulus
    stimulus <- fixations_df$Stimuli[row]
    #get the fixation point
    fix_x <- fixations_df$Fixation.X[row]
    fix_y <- fixations_df$Fixation.Y[row]
    
    
    #check if the fixation is within an AOI
    aois <- filter(aoi, Stimuli == stimulus)

    fixation_point <- c(fix_x, fix_y)
    
    #for all aoi's check if the fixation is within the aois
    for (i in seq(1,nrow(aois))){
      print(paste0("current row is ", row, " of ", nrow(fixations_df)))
        #get the points of the aoi
        string_points <- aois$Points[i]
        split_string <- strsplit(string_points, ":")
        number_of_points <- length(split_string[[1]])

        #create a matrix with the points
        points <- matrix(nrow = number_of_points/2+1, ncol = 2)
        for (j in seq(1:number_of_points)){
            #every other point is a x coordinate, the other is a y coordinate
            if (j %% 2 == 0){
                points[j/2,2] <- as.numeric(split_string[[1]][j])
            } else {
                points[(j+1)/2,1] <- as.numeric(split_string[[1]][j])
            }
        }
        points[number_of_points/2+1,] <- points[1,]

        # Check if the point is inside the polygon
        is_inside <- point.in.polygon(fixation_point[1], fixation_point[2], points[,1],points[,2])
        print(is_inside)

        if (is_inside == 1){
          if (aois$AOI.Name[i]=="Torso"|aois$AOI.Name[i]=="Tail"){
          fixations_df$AOI_hit[row] <- "Torso+Tail"
          }else if (aois$AOI.Name[i]=="Head+neck"|aois$AOI.Name[i]=="Headdress"){
            fixations_df$AOI_hit[row] <- "Head+Extensions"
          }else if (aois$AOI.Name[i]=="Frontlegs"|aois$AOI.Name[i]=="Backlegs"){
            fixations_df$AOI_hit[row] <- "Legs"
          }
          break
        }else{
          fixations_df$AOI_hit[row] <- "none"
        }
    }
}

fixations_df <- fixations_df[fixations_df$AOI_hit != "none",]

write.csv(fixations_df,"fixations_MAGNIFISO.csv")
```

# Make model dataframes
```{r}
#load relevant dataframe
fixations_df <- read.csv("fixations_MAGNIFISO.csv")
#define dataframes

first_visit <- subset(fixations_df,select = c(ID,Task, Trial_index,Stimuli, AOI_hit, Fixation.Index))

dwell_por <- subset(fixations_df,select = c(ID,Task, Trial_index,Stimuli, AOI_hit, Fixation.Duration))

fix_por <- first_visit
```

## Update DWELL%
```{r}
dwell_por$Dwell_TRIAL <- NA
dwell_por$Dwell_por <- NA

df_updated <- dwell_por%>%
  group_by(ID, Task, Trial_index) %>%
  mutate(Dwell_TRIAL = sum(Fixation.Duration)) %>%
  ungroup()

again <- df_updated %>% 
  mutate(Dwell_por = Fixation.Duration/Dwell_TRIAL)

#Index and factorise
again$ID <- as.factor(again$ID)#levels 
again$ID  <- as.numeric(again$ID)#assigning the level by overwriting the id.
again$ID  <- as.factor(again$ID)

again <- again %>%
  mutate_all(~str_replace_all(., "\\+", ""))


write.csv(again,"DWELL_PROPORTION.csv")
```

## Update fix%
```{r}
df_counts <- fix_por %>%
  group_by(ID, Task, Trial_index) %>%
  mutate(
    No_fix = n(),
    No_fix_torso = sum(AOI_hit == "Torso+Tail", na.rm = TRUE),
    No_fix_head = sum(AOI_hit == "Head+Extensions", na.rm = TRUE),
    No_fix_legs = sum(AOI_hit == "Legs", na.rm = TRUE),
  )

once <- df_counts %>% 
    mutate(fix_por_torso = No_fix_torso/No_fix,
    fix_por_head = No_fix_head/No_fix,
    fix_por_legs =No_fix_legs/No_fix
    )

twice <- once %>% 
  group_by(ID,Task,Trial_index) %>% 
  slice(1)

write.csv(twice,"FIXATION_PROPORTION.csv")

```

### Do an inspection of fixation durations
```{r}
df <- fixations_MAGNIFISO
df$ID <- as.factor(df$ID)
df$Task <- as.factor(df$Task)
df$Trial_index <- as.factor(df$Trial_index)

test <- fixations_MAGNIFISO %>% 
  group_by(ID,Task,Trial_index) %>% 
  slice(1)

test %>%
  ungroup() %>%
  filter(Fixation.Duration>mean(Fixation.Duration)) %>% 
  summarise(n())
#39%

test %>% 
  ungroup() %>% 
  filter(Fixation.Duration>200) %>% 
  summarise(n())
#63%
```

## Update first-hit
```{r}
first_hit <- first_visit %>%
  mutate(First_visit=0)
first_hit$rowno <- seq(1,nrow(first_hit))
first_hit$AOI <- NA

df_updated <- first_hit %>%
  group_by(ID, Task, Trial_index) %>%
  mutate(
    First_visit = ifelse(Fixation.Index == min(Fixation.Index), 1, 0),
    AOI = ifelse(Fixation.Index == min(Fixation.Index), AOI_hit, AOI)
  ) %>%
  ungroup()

#make the dataframe nice
first <- df_updated %>% 
  filter(First_visit==1)
new <- first

availiable_aoi <- c("Torso+Tail","Head+Extensions","Legs")
for (row in seq(1,nrow(first))){
  line <- first[row,]
  taken_aoi <- line$AOI
  availiable_aoi <- availiable_aoi[availiable_aoi != taken_aoi]
  line$First_visit=0
  line$AOI=availiable_aoi[1]
  new <- rbind(new,line)
  line$AOI=availiable_aoi[2]
  new <- rbind(new,line)
  availiable_aoi <- c("Torso+Tail","Head+Extensions","Legs")

}

xtabs(~AOI+First_visit,new) #fixed

new <- subset(new,select=c(ID,Task,Trial_index,Stimuli,AOI,First_visit))

#Index and factorise
new$ID <- as.factor(new$ID)#levels 
new$ID  <- as.numeric(new$ID)#assigning the level by overwriting the id.
new$ID  <- as.factor(new$ID)

new <- new %>%
  mutate_all(~str_replace_all(., "\\+", ""))

write.csv(new,"FIRST_VISIT.csv")
```

# Calculate AOI sizes
#AOI sizes
```{r}
#make DF for it
aoi <- subset(AOI,select=c("Stimuli","AOI.Name","Color","Points"))
#change color names
aoi$Color <- gsub("#009BBB","#6E0955", aoi$Color)
aoi$Color <- gsub("#D4A281","#009BBB", aoi$Color)
aoi$Color <- gsub("#99366","#7E5738", aoi$Color)
aoi$Color <- gsub("#E8CFAA","#009BBB", aoi$Color)
aoi$Points[32] <- NA

new_aoi <- data.frame()
for (line in seq(1,nrow(aoi)) ){
  points <- aoi$Points[line]
  if (is.na(points)){
        next
      }else{
  point <- strsplit(points, ":")
  x <- c()
  y <- c()
  for (index in seq(1,length(point[[1]]))){
          #for index that is odd, add to x vector
          if (index %% 2 == 0){
              y <- c(y,point[[1]][index])
          } else {
              x <- c(x, point[[1]][index])
          }
      }
  len <- length(x)
  new <- data.frame(stim = rep(aoi$Stimuli[line],len),
                        AOI.Color = rep(aoi$Color[line],len), 
                        AOI.Name = rep(aoi$AOI.Name[line],len),
                        x = x,
                        y = y)
      #get the first row of the new dataframe
  new <- rbind(new,new[1,])
    #bind with the other dataframes
  new_aoi <- rbind(new_aoi, new)
      }
}

aoi$aoi <- 0
for (line in seq(1,nrow(aoi))){
  if (aoi$AOI.Name[line] =="Headdress"|aoi$AOI.Name[line] =="Head+neck"){
    aoi$aoi[line] <- "head"
  }else if (aoi$AOI.Name[line]=="Torso"|aoi$AOI.Name[line]=="Tail"){
    aoi$aoi[line] <- "torso"
  }else if (aoi$AOI.Name[line]=="Frontlegs"|aoi$AOI.Name[line]=="Backlegs"){
    aoi$aoi[line] <- "legs"
  }
}

# Install and load the sp and rgeos packages
install.packages("splancs")
library(splancs)

new_aoi$x <- as.numeric(new_aoi$x)
new_aoi$y <- as.numeric(new_aoi$y)
aoi <- aoi %>% mutate(area=0)

for (line in seq(1,nrow(aoi)) ){
   if (is.na(aoi$Points[line])){
        next
      }else{
  stim <- aoi$Stimuli[line]
  ao <- aoi$AOI.Name[line]
  c <- new_aoi[new_aoi$AOI.Name==ao,] 
  c <- c[c$stim==stim,]
  x <- c$x
  y <- c$y
  t <- cbind(x,y)
  a <- splancs::areapl(t)
  
  aoi$area[line] <- a
        } 
}

aoi$aoi <- as.factor(aoi$aoi)
c <- aoi %>% 
  group_by(Stimuli,aoi) %>% 
  summarise(sum(area))

c$prop_torso <- 0

for (animal in unique(aoi$Stimuli)){
  ha <- c$`sum(area)`[c$Stimuli==animal&c$aoi=="head"]
  ta <- c$`sum(area)`[c$Stimuli==animal&c$aoi=="torso"]
  la <- c$`sum(area)`[c$Stimuli==animal&c$aoi=="legs"]
  ht <- ((ha-ta)/ta)*100
  lt <- ((la-ta)/ta)*100
  c$prop_torso[c$aoi=="head"&c$Stimuli==animal] <- ht
  c$prop_torso[c$aoi=="legs"&c$Stimuli==animal] <- lt
}

c %>% 
  group_by(aoi) %>% 
  summarise(mean(prop_torso))
```

# Heat maps
## Load data
```{r}
aoi <- read.csv("AOI_MAGNIFISO.csv") #clean as in AOI clean up

#change color names
aoi$Color <- gsub("#009BBB","#6E0955", aoi$Color)
aoi$Color <- gsub("#D4A281","#009BBB", aoi$Color)
aoi$Color <- gsub("#99366","#7E5738", aoi$Color)
aoi$Color <- gsub("#E8CFAA","#009BBB", aoi$Color)
```

## Define colours
```{r}
heat_colors <- colorRampPalette(
  c(
    "#00007F",
    "blue",
    "#007FFF",
    "cyan",
    "#7FFF7F",
    "yellow",
    "#FF7F00",
    "red",
    "#7F0000"
  )
)

aoi_colors <- c( 
                      "TorsoTail"= "#009BBB",
                      "HeadExtension"= "#6E0955",
                      "Legs"= "#7E5738"
                      )
```

## Define size of images:
```{r}
img_size <- read.csv("img_size.csv")
img_size$stim <- gsub(".jpg","",img_size$stim)
img_size$stim <- gsub("11","4",img_size$stim)
write.csv(img_size,"img_size.csv")
```

## Heatmap function
```{r}
img_size <- read.csv("img_size.csv")
df <- read.csv("fixations_MAGNIFISO.csv")
d <- subset(df,select=c("ID","Task","Trial_index","Stimuli","AOI_hit","Fixation.Index","Fixation.X","Fixation.Y"))
d$Task <- gsub("style", "Aesthetic", d$Task)
d$Task <- gsub("act", "Movement", d$Task)
d$Task <- gsub("recog", "Species", d$Task)
d$AOI_hit <- gsub("\\+","",d$AOI_hit)

make_heatmap <- function(participant, stimulus,task){
  #find relevant data
  hov<- d[d$ID == participant & d$Stimuli == stimulus & d$Task==task,]
  trials = unique(hov$Trial_index)
  z <- hov[hov$Trial_index==trials[-1],]
    
  #import the image corresponding to the trial
  img <- jpeg::readJPEG(paste0('experiment_images/out/', z$Stimuli[1],".jpg")) 
  img <- grid::rasterGrob(img, width=unit(1, "npc"), height = unit(1,"npc"), interpolate = FALSE)
  
  stimulus <- z$Stimuli[1]
      
    #make coordinates
    ## the screen was 1920x1080 (XxY)
    ## the image was centered
    ymx <- (1080-img_size$ypix[img_size$stim==stimulus])/2+img_size$ypix[img_size$stim==stimulus]
    xmx <- (1920-img_size$xpix[img_size$stim==stimulus])/2+img_size$xpix[img_size$stim==stimulus]
    ym <- (1080-img_size$ypix[img_size$stim==stimulus])/2
    xm <- (1920-img_size$xpix[img_size$stim==stimulus])/2
    
    #flip y-axis
    z$Fixation.Y <- 1080 - z$Fixation.Y
    
    #make plot
    p <- ggplot(z, aes(Fixation.X, Fixation.Y, color = Fixation.Index)) + 
        annotation_custom(img, xmin = xm, xmax = xmx, ymin = ym, ymax = ymx) +
        #annotate(geom = "rect", xmin = 0, xmax = 1920, ymin = 0, ymax = 1080, colour = "#D4A281", fill="white",alpha = 0.0) +
        stat_density2d(geom = "raster", aes(fill = ..density.., alpha = sqrt(sqrt(..density..))), contour = FALSE, n = 1000) + 
    scale_fill_gradientn(colours = heat_colors(10), trans="sqrt") +
    scale_alpha(range = c(0.1, 0.6)) +
    xlim(xmin = 0, xmax = 1920) +ylim(ymin = 0, ymax = 1080) +
        labs(title=NULL,x=NULL,y=NULL)+#=paste0("ID ", participant, " in the ",task," task")
    theme(text=element_text(family="Cambria"))+
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank())+
      theme(legend.position = "none")+
      theme(axis.text.x=element_blank(), 
      axis.ticks.x=element_blank(), 
      axis.text.y=element_blank(), 
      axis.ticks.y=element_blank())+
      guides(fill = guide_legend(override.aes = list(title = NULL))) +
    guides(alpha = guide_legend(override.aes = list(title = NULL)))

    print(p)
    ggsave(paste0(participant,"_",task,"_",stimulus,".jpg"),width = 16, height = 9, units = "in")
}
```

## Draw heatmaps example
```{r}
for (ID in unique(d$ID)){
  make_heatmap(ID,"bison_10","Aesthetic")
}
```
